---
title: "Programmatic Tabsets using Knitr Engine"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knitr-tabset}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
#| include: false
library(jcutils)
jcutils::knitr_default_setup(echo = TRUE)
```

This vignette showcases the ability to output a list to a knitr report 
    (Quarto or R Markdown) in the form of a tabset.
Unfortunately, tabs are not available in Vignettes and will not display 
    properly but the output still serve as an example.

We make use of the `mtcars` dataset to illustrate typical usage.

```{r}
data("mtcars", package = "datasets")
vars <- stats::setNames(nm = c("disp", "hp", "drat"))
```

## Signature

```{.r}
jcutils::knitr_tabset(.x, .f, type = c("quarto", "rmd"), ...)
```

- `.x` is a list to loop through; it is advised to pass a named list for tab 
  headings but can be omitted to use numerical labelling;
  
- `.f` is a function or formula similar in operation to `purrr::walk`;

- `...` also behaves like `purrr` methods for passing arguments to `.f`;

- `.type` is required to ensure output works correctly for Quarto or R Markdown.

## Plots (`ggplot2`)

```{r plotlist}
plotlist <- 
  lapply(vars, function(.x) ggplot2::qplot(mtcars$mpg, mtcars[[.x]]))
```

Unnamed list example.

```{r plotlist-tabs-unnamed}
#| results: asis
jcutils::knitr_tabset(unname(plotlist), type = "rmd")
```

Named list example.

```{r plotlist-tabs-named}
#| results: asis
jcutils::knitr_tabset(plotlist, type = "rmd")
```

## Tables (`gt`)

Printing a `gt` object (the default) leads to issues so we convert it to raw
    HTML and pipe it through `cat`.

```{r gtlist}
gtlist <- 
  lapply(vars, function(.x) gt::gt(mtcars[1:5, .x, drop = FALSE]))
```

```{r gtlist-tabs}
#| results: asis
jcutils::knitr_tabset(gtlist, ~ cat(gt::as_raw_html(.x)), type = "rmd")
```

## Tables (`kable`)

```{r kablelist}
kablelist <-
  lapply(vars, function(.x) knitr::kable(mtcars[1:5, .x, drop = FALSE]))
```

```{r kablelist-tabs}
#| results: asis
jcutils::knitr_tabset(kablelist, type = "rmd")
```
