---
title: "Dynamic Tabsets using Knitr Engine"
author: "Josh Cowley"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    self-contained: true
---

```{r setup}
#| include: false
library(ggplot2)
library(jcutils)
jcutils::knitr_default_setup(echo = TRUE)
```

This vignette showcases the ability to output a list to a knitr report 
    (Quarto or R Markdown) in the form of a tabset.

In the case of an unnamed list, the method defaults to numerical labelling.

We make use of the `mtcars` dataset to illustrate typical usage.

```{r}
data("mtcars", package = "datasets")

vars <- stats::setNames(nm = c("disp", "hp", "drat"))

gg_mtcars <- function(.x, ...) {
  ggplot2::qplot(mtcars[[.x]], mtcars$mpg, xlab = .x, ...)
}
```

## Usage

To affect all lists within a document, one can register a method for the S3 
    generic `knit_print` which is explained [here][knit_print_vignette].

```{r}
#| echo: true
library(knitr)
registerS3method("knit_print", "list", jcutils::printer_tabset)
```

Affecting a single chunk is achieved through the `render` chunk option.

````markdown
```{r}`r ''`
#| render: !expr jcutils::printer_tabset
myList
```
````

::: {.callout-note}
We don't pass the list to `print` but rather make it visible either by calling 
    its reference name or a function that returns said list.
::::

## Plots (`ggplot2`)

```{r plotlist}
plotlist <- lapply(vars, gg_mtcars)
```

### Unnamed List

```{r plotlist-tabs-unnamed}
unname(plotlist)
```

### Named List

```{r plotlist-tabs-named}
plotlist
```

### Nested List

Nested lists work in Quarto but not in Rmd format.
  See [#11](https://github.com/nclJoshCowley/jcutils/issues/11)

## Tables (`gt`)

```{r gtlist}
gtlist <- 
  lapply(vars, function(.x) gt::gt(mtcars[1:5, c(.x, "mpg"), drop = FALSE]))
```

```{r gtlist-tabs}
gtlist
```

## Tables (`kable`)

```{r kablelist}
kablelist <-
  lapply(vars, function(.x) knitr::kable(mtcars[1:5, c(.x, "mpg"), drop = FALSE]))
```

```{r kablelist-tabs}
kablelist
```


[knit_print_vignette]:
  https://cran.r-project.org/web/packages/knitr/vignettes/knit_print.html
  "Knitr - Custom Print Methods"
